\begin{rubric}{Grants, Honours and Scholarships}
  \entry*[2025] \textbf{Tokyo Metropolitan University, Funds for Research Stay
    in Overseas}. Living expenses are covered by Tokyo
  Metropolitan University Fund.
  \entry*[2025] \textbf{Graint-in-Aid for Early-Career Scientists}. Research expenses are convered by KAKENHI.
  \entry*[2024] \textbf{Graint-in-Aid for Research Activity Start-up}. Research expenses are convered by KAKENHI.
  \entry*[2023] \textbf{Long-Term Performance Award.}
  Award from IBM, based on skills needed for the future, long-term caree potential, and strong indivisual performance.
  \entry*[2023] \textbf{Research Fellowship for Young Scientists (JSPS PD).}
  Fellowship from the Japan Society for the Promotion of Science (JSPS), covering
  living expenses. Research expenses covered by KAKENHI. (declined)
  \entry*[2021] \textbf{Research Fellowship for Young Scientists (JSPS DC2)}.
  Fellowship from the Japan Society for the Promotion of Science (JSPS), covering
  living expenses. Research expenses covered by KAKENHI.
  \entry*[2020] \textbf{JST Strategic Basic Research Programs ACT-X}. Research
  expenses covered by Japan Science and Technology Agency (JST).
  %\entry*[2020] \textbf{Tokyo Tech Tsubame Scholarship for Doctoral
  %  Students}. Covering living expenses.
  %\entry*[2019] \textbf{Travel Grants by Information Science Incentive Fund}. By
  %dept. of mathematical and computing science, Tokyo Tech.
  \entry*[2019] \textbf{2nd Place, Graduate Category, ACM Student Research
    Competition, \textit{Association for Computing Machinery}. [*]}
  %\entry*[2014] \textbf{Scholarship by the Showa Scholarship Foundation}. Covering
  %living expensed by Showa Scholarship Foundation.
\end{rubric}
